Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-05 abstract.tex

The correlations between event-by-event fluctuations of amplitudes of anisotropic flow harmonics 
have been measured in $\PbPb$ collisions at $\snn=2.76$~TeV with the ALICE detector at the Large Hadron Collider. 
The results were obtained with the multi-particle correlation observables dubbed symmetric cumulants.
These observables are robust against systematic biases originating from non-flow effects. 
The centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$ and $v_5$) and the lower order harmonics ($v_2$ and $v_3$) as well as the transverse momentum dependence of correlations of $v_3$ and $v_2$ and $v_4$ and $v_2$ correlations are presented. 
The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) model calculations.
The comparison to viscous hydrodynamic model demonstrates that
the different order harmonic correlations respond differently to the initial conditions or the shear viscosity to the entropy density ratio ($\eta/s$). The small $\eta/s$ regardless of initial conditions is favored and the small $\eta/s$ with the AMPT initial condition is closest to the measurements. 
Correlations between $v_2$ , $v_3$ and $v_4$ magnitudes show moderate $p_{\rm T}$ dependence in mid-central collisions. This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out, which might help to understand possible contribution of bulk viscosity in a hadronic phase of the system.
Together with the existing measurements of individual flow harmonics the presented results provide further constraints 
on initial conditions and the transport properties of the system produced in heavy-ion collisions.

>>>>

The correlations between event-by-event fluctuations of amplitudes of anisotropic flow harmonics 
have been measured in $\PbPb$ collisions at $\snn=2.76$~TeV with the ALICE detector at the Large Hadron Collider. 
The results were obtained with the multi-particle correlation observables dubbed symmetric cumulants.
These observables are robust against systematic biases originating from non-flow effects. 
The centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$ and $v_5$) and the lower order harmonics ($v_2$ and $v_3$) as well as the transverse momentum dependence of correlations of $v_3$ and $v_2$, $v_4$ and $v_2$ correlations are presented. 
The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) model calculations.
The comparison to viscous hydrodynamic model demonstrates that
the different order harmonic correlations respond differently to the initial conditions or the temperature dependence of the shear viscosity to the entropy density ratio ($\eta/s$). The small $\eta/s$ regardless of initial conditions is favored and the small $\eta/s$ with the AMPT initial condition is closest to the measurements. 
Correlations between $v_2$, $v_3$ and $v_4$ magnitudes show moderate $p_{\rm T}$ dependence in mid-central collisions. This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out, which might help to understand possible contribution of bulk viscosity in a hadronic phase of the system.
Together with the existing measurements of individual flow harmonics the presented results provide further constraints 
on initial conditions and the transport properties of the system produced in heavy-ion collisions.
